Assigning Boy Scouts to Patrols

### 2016-06-03 poster/poster.tex
all the scouts pic

% Section and subsections will appear in the presentation overview
% and table of contents.
\begin{frame}{Problem Description}%{Optional Subtitle}
	\begin{itemize}
		\item Scoutmaster Gene Bruce of Troop 407 in Kent, Washington must assign new boy scouts into their patrols. In these patrols, the scouts engage in numerous activities and form close bonds. \\
		\vspace{0.2in}
		\item The number of incoming scouts are increasing requiring multiple patrols to better organize activities and to form a small community between scouts.
		The younger scouts are temperamental and awkward when dealing with adversity, ruining their experience and causing many to quit. \\
		\vspace{0.2in}
		\item \textbf{Goal:  Assign 13 boy scouts of appropriate size (of 6-8 scouts) to two patrols such that we maximize the retention rate of the scouts by avoiding severe conflicts and maximizing positive relationships between scouts.}
	\end{itemize}
\end{frame}

\begin{frame}{Simplifications}
	\begin{itemize}
		\item Instead of considering the scouts' complex personality and their interactions with other scouts, we simplified by only asking each scout which other scouts they liked or disliked.
		\vspace{0.5in}
		\item Quality of the a patrol can be determined by the quality of the relationships between the unique pairs of the group. \\
		\textbf{i.e.} the whole is equal to the sum of its parts.
	\end{itemize}
\end{frame}

\begin{frame}{Acknowledgments}
	We would like to sincerely thank:
	\vspace{0.2in}
	\begin{itemize}
		\item \textbf{Scoutmaster Gene Bruce} for providing us the data and being extremely patient and understanding when discussing the background and problem.
		\vspace{0.2in}
		\item \textbf{Professor Sara Billey} for the mentorship and guidance throughout the entire project.
		\vspace{0.2in}
		\item \textbf{Austin Tran} for his helpful comments and suggestions.
	\end{itemize}
\end{frame}
% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{A Mathematical Interpretation}
1 enemy + 1 enemy = 0 survivors  
\end{frame}

>>>>

% Section and subsections will appear in the presentation overview
% and table of contents.
\begin{frame}{Problem Description}%{Optional Subtitle}
	\begin{itemize}
		\item Scoutmaster Gene Bruce of Troop 407 in Kent, Washington must assign new boy scouts into their patrols. In these patrols, the scouts engage in numerous activities and form close bonds. \\
		\vspace{0.2in}
		\item The number of incoming scouts are increasing, requiring multiple patrols to better organize activities and to form a small community between scouts.
		The younger scouts are temperamental and awkward when dealing with adversity, ruining their experience and causing many to quit. \\
		\vspace{0.2in}
		\item \textbf{Goal:  Assign 13 boy scouts of appropriate size (of 6-8 scouts) to two patrols such that we maximize the retention rate of the scouts by avoiding severe conflicts and maximizing positive relationships between scouts.}
	\end{itemize}
\end{frame}

\begin{frame}{Simplifications}
	\begin{itemize}
		\item Instead of considering the scouts' complex personality and their interactions with other scouts, we simplified by only asking each scout which other scouts they liked or disliked.

		\item Add last simplification
	\end{itemize}
\end{frame}

% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{A Mathematical Interpretation}
1 enemy + 1 enemy = 0 survivors  
\end{frame}
